Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-09 Paper/paper.tex
Update last sentence of abstract

The effect of target policies is investigated justifying the use of these to align the interests of individual hospitals and social welfare.
In particular, we identify the lowest value of a utilisation target that aligns these.
\end{abstract}

>>>>

In the UK a variety of utilisation targets are often discussed: aiming to ensure that wards/hospitals operate at a given utilisation value.
The effect of these target policies is investigated justifying their use to align the interests of individual hospitals and social welfare.
In particular, we identify the lowest value of a utilisation target that aligns these.
\end{abstract}
